### 2015-05-23 docs/report/map_serial_vs_parallel.tex

Since as explained in \ref{sec:serialization-and-transference} the cost of transferring objects is not zero, it is important to compare the performance of our parallel implementation against a serial one.

In this regard, the more complex the computation to be performed on each array element the better the parallel implementation will perform. That is because in the parallel case, the source \ttarray{} must be copied to sub-arrays in order to be transferred. On the contratry, the serial implementation can take that time to actually operate on some elements.

@@

\note{Unlike other benchmarks in which we were comparing different ways to achieve the same, this benchmark compares the same thing with different element amounts. That's why the original charts are not displayed.}

>>>>

Since as explained in Section~\ref{sec:serialization-and-transference} the cost of transferring objects is not zero, it is important to compare the performance of our parallel implementation against a serial one.

In this regard, the more complex the computation to be performed on each array element the better the parallel implementation will perform. That is because in the parallel case, the source \ttarray{} must be copied to sub-arrays in order to be transferred. On the contrary, the serial implementation operates on elements during that time.

@@

\note{Unlike other benchmarks in which we were comparing different ways to achieve the same result, this benchmark compares a single way with a changing amount of elements. For that reason, the original charts are not displayed.}

### 2015-05-23 docs/report/modules.tex

\note{At the time of writing, Google Chrome does not support the ES6 module specification so that is not a viable choice.}

@@

Instead of making the choice for users, our library will support both systems in a way that is easy for users.

\subsection{CommonJS support}
All that needs to be done to use the library is shown in the following code snippet:
\begin{lstlisting}[language=HTML, caption=CommonJS usage]
<script src="https://rawgit.com/pjsteam/pjs/v0.2.1/dist/p-j-s.min.js"></script>

@@

The file \textbf{main.js} must have the following contents:
\begin{lstlisting}[caption=main.js AMD support]
require(["https://rawgit.com/pjsteam/pjs/v0.2.1/dist/p-j-s-standalone.min.js"], function(pjs) {
  pjs.init();

>>>>

\note{At the time of writing, neither Google Chrome nor Mozilla Firefox support the ES6 module specification so that is not a viable choice.}

@@

Instead of making the choice for users, our library will support both systems in a way that makes it easier for users to consume either of them.

\subsection{CommonJS support}
All that needs to be done to use the library is shown in the following code snippet:
\begin{lstlisting}[language=HTML, caption=CommonJS usage]
<script src="https://rawgit.com/pjsteam/pjs/v1.0.0-beta/dist/p-j-s.min.js"></script>

@@

The file \textbf{main.js} must have the following contents:
\begin{lstlisting}[caption=main.js AMD support]
require(["https://rawgit.com/pjsteam/pjs/v1.0.0-beta/dist/p-j-s-standalone.min.js"], function(pjs) {
  pjs.init();
